Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-04-29 paper/figures.tex
Add http-www figure

\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 3,
		horizontal sep=8pt,
		vertical sep=16pt,
	},
]

@@

\nextgroupplot[
	title=(c) Origin HTTP response codes,
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpsWwwDatasetsYbar,
	width=.55\textwidth,
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Sec}{Secure}{green}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mix sec}{Mixed}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Insec}{Insecure}{orange}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mism}{Mismatch}{lightgray}{}

@@

\nextgroupplot[
	title=(c) Origin HTTP response codes,
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpsWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Sec}{Secure}{green}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mix sec}{Mixed}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Insec}{Insecure}{orange}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mism}{Mismatch}{lightgray}{}

@@

>>>>

\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 4,
		horizontal sep=8pt,
		vertical sep=16pt,
	},
]

@@

\nextgroupplot[
	title=(c) Origin HTTP response codes,
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpsWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mix sec}{3xx Mixed}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Insec}{3xx Insecure}{red}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mism}{3xx Mismatch}{lightgray}{}

@@

\nextgroupplot[
	title=(c) Origin HTTP response codes,
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpsWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mix sec}{3xx Mixed}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Insec}{3xx Insecure}{red}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mism}{3xx Mismatch}{lightgray}{}

@@

\nextgroupplot[
	title=(d) Origin HTTP response codes,
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpWwwDatasetsYbar,
	width=.55\textwidth,
]

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{2xx}{2xx}{green}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{3xx}{3xx}{yellow}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{(null)}{(null)}{red}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Mix sec}{3xx Mixed}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Insec}{3xx Insecure}{orange}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Mism}{3xx Mismatch}{lightgray}{}

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww;
\addlegendentry{Final redirect secure}

\nextgroupplot[
	title=(d) Origin HTTP response codes,
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
]

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{2xx}{2xx}{green}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{3xx}{3xx}{yellow}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{(null)}{(null)}{red}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Mix sec}{3xx Mixed}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Insec}{3xx Insecure}{orange}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Mism}{3xx Mismatch}{lightgray}{}

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww;
\addlegendentry{Final redirect secure}

### 2015-04-29 paper/tableread.tex
Add http-www figure

>>>>

%%% Sweden http-www

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.classification.domain-scope.coverage.sorted.sweden-http-www.tsv}\tableDatasetsNonFailedClassificationDomainScopeCoverageSortedSwedenHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.disconnect.organizations.coverage.external.sorted.sweden-http-www.tsv}\tableDatasetsNonFailedDisconnectOrganizationsCoverageExternalSortedSwedenHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.disconnect.categories.coverage.external.sorted.sweden-http-www.tsv}\tableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedSwedenHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.request-status.coverage.origin.sorted.sweden-http-www.tsv}\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.origin-redirects.coverage.sorted.sweden-http-www.tsv}\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww

%%% Global http-www

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.classification.domain-scope.coverage.sorted.global-http-www.tsv}\tableDatasetsNonFailedClassificationDomainScopeCoverageSortedGlobalHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.disconnect.organizations.coverage.external.sorted.global-http-www.tsv}\tableDatasetsNonFailedDisconnectOrganizationsCoverageExternalSortedGlobalHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.disconnect.categories.coverage.external.sorted.global-http-www.tsv}\tableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedGlobalHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.request-status.coverage.origin.sorted.global-http-www.tsv}\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.origin-redirects.coverage.sorted.global-http-www.tsv}\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww
